\documentclass{article}
\usepackage{graphicx} 
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{arydshln}
\usepackage[a4paper, margin=1in]{geometry}

\title{Laboratory 2}
\author{Víctor Brull\and
        Guillem Martínez}
\date{April 2026}

\begin{document}

\maketitle

\section{Introduction}

Image feature matching is a key step in many computer vision tasks, such as
3D reconstruction, SLAM, visual localization, and panorama stitching. The goal of
this laboratory is to find reliable point correspondences between two or more images of the 
same scene, which may differ in viewpoint, scale, rotation, or illumination.

The most classical approach uses hand-crafted local feature descriptors. Among
them, SIFT~\cite{Lowe2004} is one of the most widely used methods. It detects
keypoints across scale space, assigns them an orientation, and describes them
with a 128-dimensional gradient histogram. This makes SIFT invariant to scale
and rotation, and partly robust to illumination changes. Since SIFT matches
always contain outliers, RANSAC is used on top of it to robustly estimate
homographies between image pairs.

Besides SIFT, many other descriptors have been developed. Binary descriptors
like ORB and BRISK are faster and suitable for real-time use. Methods like SURF
speed up detection with integral images, while FAST uses minimal computation.
However, all these methods share a key limitation: each descriptor is computed
locally, without any knowledge of the other image. This makes them unreliable
in textureless regions, repetitive patterns, or under motion blur.

To overcome this, LoFTR~\cite{Sun2021} uses a Transformer with self-attention 
to build dense correspondences at coarse resolution, then refines them to sub-pixel
accuracy. Its global receptive field allows matching even in low-texture regions
where classical detectors fail. Moreover, LightGlue~\cite{Lindenberger2023}
introduces a sparse deep matcher that works on top of any local detector. It
uses adaptive depth and width to stop early on easy pairs and prune poor
keypoints, achieving high accuracy at lower computational cost.

This report is organized as follows. Section~\ref{sec:Methods} describes the
theoretical background of each method. Section~\ref{sec:Experiments} presents
results for SIFT-based homography estimation and mosaicking, a comparison of
classical descriptors under synthetic transformations, and an evaluation of
LoFTR and LightGlue on challenging image pairs. Finally, Section~\ref{sec:Conclusion} 
draws conclusions and discusses the trade-offs between classical and data-driven pipelines.

\section{Methods}

Use report of lab 1 to describe the methods used in this lab. You can also add a 
description of the LoFTR and LightGlue methods, as well as any other methods you 
have used in your experiments.


\section{Experiments}



\section{Conclusion}




\bibliographystyle{IEEEbib}
\bibliography{references}

\end{document}
